Algebraic Topology Final Report: Morse Theory

### 2013-01-15 paper.tex
start working on the last section

\newcommand{\bd}[1]{\mathbf{#1}}  % for bolding symbols
\newcommand{\RR}{\mathbb{R}}      % for Real numbers
\newcommand{\ZZ}{\mathbb{Z}}      % for Integers
\newcommand{\col}[1]{\left[\begin{matrix} #1 \end{matrix} \right]}
\newcommand{\comb}[2]{\binom{#1^2 + #2^2}{#1+#2}}
\newcommand{\vect}[1]{\vec{#1}}

@@

As an application of the previous results,

>>>>

\newcommand{\bd}[1]{\mathbf{#1}}  % for bolding symbols
\newcommand{\RR}{\mathbb{R}}      % for Real numbers
\newcommand{\ZZ}{\mathbb{Z}}      % for Integers
\newcommand{\CC}{\mathbb{C}}
\newcommand{\col}[1]{\left[\begin{matrix} #1 \end{matrix} \right]}
\newcommand{\comb}[2]{\binom{#1^2 + #2^2}{#1+#2}}
\newcommand{\vect}[1]{\vec{#1}}

@@

As an application of the previous results, we will prove the Lefschetz theorem
on hyperplane sections in this section. Before the development, we should show
that every complex analytic manifold can be viewed as a CW-complex:

\begin{thm}
  A complex manifold analytic manifold $M$ of complex dimension $k$,
  bianalytically embedded as a closed subset of $\CC^n$ has the homotopy type of
  a $k$-dimensional CW-complex.
\end{thm}

The proof will be broken up into several steps. First we consider a quadratic
form in $k$ complex variables
\begin{equation}
  Q(z^1, .., z^k) = \sum b_{hj}z^hz^j.
\end{equation}

If we substitute $x^h+iy^h$ for $z^h$ and take the real part of $Q$, we obtain a
real quadratic form in $x^1, .., x^k, y^1, .., y^k$:

\begin{equation}
  Q'(x^1, .., x^k, y^1, .., y^k) = Re\{\sum b_{hj}z^hz^j\}.
\end{equation}

\begin{asser}
  If $e$ is an eigenvalue of $Q'$ with multiplicity $\mu$, then $-e$ is also an
  eigenvalue with the same multiplicity $\mu$.
\end{asser}

\begin{proof}
  First we note that $Q(iz^1, .., iz^k) = -Q(z^1, .., z^k)$. Therefore, in terms
  of $Q'$, we have
  \begin{equation}
    -Q' = J^TQ'J
  \end{equation}
  where
  \begin{equation}
    J = 
    \left(
      \begin{matrix}
        O & -I_k \\
        I_k & O
      \end{matrix}
    \right)
  \end{equation}
  is an orthogonal matrix. Therefore
  \begin{equation}
    \begin{aligned}
      det(eI-Q') = 0 &\Leftrightarrow det(eI-J^TQ'J) = 0 \\
      &\Leftrightarrow det(eI+Q') = 0.      
    \end{aligned}
  \end{equation}
\end{proof}

Now consider a complex manifold $M$ which is bianalytically embedded as a subset
of $\CC^n$. Let $q$ be a point of $M$.

\begin{asser}
  The focal points of $(M, q)$ along any normal lines $\mathbb{l}$ ocur in pairs
  which are situated symmetrically about $q$.
\end{asser}

\begin{proof}
